|

### 2023-04-23 manuscript/Chapter2-SupInfo.Rmd
update supmat added tables for bias test

output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

@@

>>>>

output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: ecology.csl
---

@@

```{r tableprep, include = FALSE}

# ===========================================================================
# 1. Extract the fixed effects from the MV model
# ===========================================================================

# Prepare the table ---------------------------------------------------------

# Model fit
fit <- readRDS(
  here::here("outputs", "02_outputs_models", "02B2_DHMLM.rds")
)

# Fixed effects table
results <- data.table(
  round(summary(fit)$fixed, digits = 3)[, 1:4],
  keep.rownames = TRUE
)

setnames(results, "rn", "parameter")

results[parameter %like% "predspeed", trait := "predator speed"][
  parameter %like% "preyavgspeed", trait := "prey speed"][
    parameter %like% "success", trait := "hunting success"
  ]

# mu parameters table
tabs1 <- results[
    !(parameter %like% "sigma"),
    c(6, 1, 2, 4, 5)
]

# sigma parameters table
tabs2 <- results[
    parameter %like% "sigma",
    c(6, 1, 2, 4, 5)
]

# Rename parameter values ---------------------------------------------------

# Rename
tabs1[,
  parameter := c(
    rep(
      c("prey rank",
        "cumulative experience",
        "group 1",
        "group 4",
        "group 2",
        "group 3"),
      2
    ),
      c("game duration",
        "cumulative experience",
        "group 1",
        "group 4",
        "group 2",
        "group 3")
  )
]
# Reorder rows
tabs1 <- tabs1[
  c(1:3, 5, 6, 4,
    7:9, 11, 12, 10,
    13:15, 17, 18, 16)
]

# Rename
tabs2[,
  parameter := rep(
    c("prey rank",
      "cumulative experience",
      "group 1",
      "group 4",
      "group 2",
      "group 3"),
    2
  )
]

# Reorder
tabs2 <- tabs2[
  c(1:3, 5, 6, 4,
    7:9, 11, 12, 10)
]

# ===========================================================================
# ===========================================================================

# ===========================================================================
# 2. Compute the table using flextable
# ===========================================================================

# Prepare the table parameters ----------------------------------------------

# Custom header
my_header <- data.frame(
   col_keys = c("trait",
                "parameter",
                "Estimate",
                "l-95% CI",
                "u-95% CI"),
   line1 = c("Trait",
             "Parameter",
             "Value",
             "lower 95% CI",
             "upper 95% CI"),
   stringsAsFactors = FALSE
)

# Custom theme
my_theme <- function(x, ...) {
   x <- colformat_double(x, big.mark = " ",
                         decimal.mark = ".",
                         digits = 2)
   x <- set_table_properties(x, layout = "fixed")
   x <- border_remove(x)
   std_border <- fp_border(width = 1, color = "black")
   x <- hline_top(x, part = "all", border = std_border)
   x <- hline_bottom(x, part = "all", border = std_border)
   autofit(x)
}

```{r tables1, ft.align = "left"}
# Create the table ----------------------------------------------------------

tabs1f <- tabs1 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs1,
    caption = "Fixed effects table on the mean part of the model",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

tabs1f

# ===========================================================================
# ===========================================================================

```{r tableS2, ft.align = "left"}

tabs2f <- tabs2 %>%
  flextable(col_keys = my_header$col_keys) %>%
  set_header_df(mapping = my_header, key = "col_keys") %>%
  my_theme() %>%
  merge_v(j = 1) %>%
  valign(j = 1, valign = "top", part = "body") %>%
  align(align = "left", part = "all", j = c(1, 2)) %>%
  align(align = "center", part = "all", j = 3) %>%
  align(align = "center", part = "all", j = 4) %>%
  align(align = "center", part = "all", j = 5) %>%
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
    ),
    ref_symbols = " "
  ) %>%
  set_caption(
    tabs2,
    caption = "Fixed effects table on the dispersion part of the model",
    style = "Table Caption"
  ) %>%
  fontsize(size = 10, part = "all") %>%
  fontsize(size = 12, part = "footer") %>%
  font(fontname = "Times New Roman", part = "all")

tabs2f
